Application of the XT3D Multi-Point Flux Approximation to Vertically Staggered Grids in MODFLOW 6 to Improve Accuracy of Simulated Flows in Steeply Dipping Layers

### 2022-09-27 latex/article.tex
* Added option to the disu_approach notebook to have the "domain" present. Refactored and expanded the setup of scenarios. * Inserted figs and captions with preliminary results of simulations with the domain present.

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid. The news is all bad; XT3D doesn't really help. (preliminary result from disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow along the channel)}
\label{fig:figures}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-cf-head.}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid and boundary heads set up for crossflow. The standard formulation is a fail, but XT3D nails it, even without cross-connections. (preliminary result from disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow across the channel)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections. The news is much better; the standard formulation isn't horrible, and XT3D nails it. (preliminary result from disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow along the channel)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-cf-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections and boundary heads set up for crossflow. The standard formulation does pretty well, and XT3D nails it again. (preliminary result from disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow across the channel)}
\label{fig:figures}
\end{figure}

@@

\subsection{Domain}
Results with the surrounding "domain" (from an updated disu\_approach notebook) are similar but not identical, apparently due to the "staircase" effect. Might be best to presnt most of our results without the domain, at least when illustrating the main problem and its solution (to keep the "theory" clear), then discuss what happens when the domain is present (which is more like in practice).

>>>>

XXXXX Results without the domain are presented first to "cleanly" illustrate the main problem and its solution. Results with the domain are then presented to give more of an indication of how things might work in practice. Unless stated otherwise, the domain is 6 orders of magnitude less conductive than the channel, as in \cite{bardot2022}. XXXXX

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid. As Kerry and Jim found previously, the news is all bad; the flow tends to go horizontal, and XT3D doesn't really help. (preliminary result from disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow along the channel; scenarios disu-af-vo-s and disu-af-vo-x)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-cf-head.}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid and boundary heads set up for crossflow. The standard formulation is a fail, but XT3D nails it, even without cross-connections. (preliminary result from disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow across the channel; scenarios disu-cf-vo-s and disu-cf-vo-x)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections. The news is much better; the standard formulation is much improved, and XT3D nails it. (preliminary result from disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow along the channel; scenarios disu-af-vs-s and disu-af-vs-x)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-cf-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections and boundary heads set up for crossflow. The standard formulation does pretty well, and XT3D nails it. (preliminary result from disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow across the channel; scenarios disu-cf-vs-s and disu-cf-vs-x)}
\label{fig:figures}
\end{figure}

\subsection{Test Problem 3: Vertically Offset Discretization with Domain}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-af-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-af-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid with the domain. Results are similar to those without the domain and consistent with what Kerry and Jim found previously; the flow tends to go horizontal, and XT3D doesn't really help. (preliminary result from disu\_approach model, 5x11 channel with 5x11 subdomains above and below, without cross-connections, $30^{\circ}$ incline, set up for flow along the channel; scenarios disu-d-af-vo-s and disu-d-af-vo-x)}
\label{fig:figures}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-cf-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-cf-head.}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-cf-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid with the domain and boundary heads set up for crossflow. The standard formulation gives nearly vertical flow in the channel, and XT3D also does poorly, even mid-channel. The huge specific discharge vectors near the channel boundary are apparently caused by XT3D's head-gradient interpolation drawing heads from the domain, where the head gradient is huge, when computing nominally horizontal flows between cells within the channel. (preliminary result from disu\_approach model, 5x11 channel with 5x11 subdomains above and below, without cross-connections, $30^{\circ}$ incline, set up for flow across the channel; scenarios disu-d-cf-vo-s and disu-d-cf-vo-x)}
\label{fig:figures}
\end{figure}

\subsection{Test Problem 4: Vertically Staggered Discretization with Domain}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-af-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-af-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with the domain and with cross-connections. The standard formulation isn't horrible, and XT3D does very well except at the channel boundary, where there's presumably a "staircase" effect. (preliminary result from disu\_approach model, 5x11 channel with 5x11 subdomains above and below, with cross-connections, $30^{\circ}$ incline, set up for flow along the channel; scenarios disu-d-af-vs-s and disu-d-af-vs-x)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-cf-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-cf-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-d-cf-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with the domain and with cross-connections and boundary heads set up for crossflow. The standard formulation is much improved. You can't tell because of the scale of the vectors, but XT3D does well mid-channel. However, near the channel boundary it still has huge flows due to interpolating heads from the domain. (preliminary result from disu\_approach model, 5x11 channel with 5x11 subdomains above and below, $30^{\circ}$ incline, set up for flow across the channel; scenarios disu-d-cf-vs-s and disu-d-cf-vs-x)}
\label{fig:figures}
\end{figure}

@@

\subsection{Domain}
Results with the surrounding "domain" (from an updated disu\_approach notebook) are similar but not identical, apparently due to the "staircase" effect. Might be best to present most of our results without the domain, at least when illustrating the main problem and its solution (to keep the "theory" clear), then discuss what happens when the domain is present (which is more like in practice).
